Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-03-24 msr/msr2011.tex
Discuss features, fix wordnet stuff, respond to example criticism
    - [X] In supervised labeling (3.3) it has not been discussed what
          features of commit messages has been used in
          training/testing learners.
          - response: in supervised labelling we described the word count
            approach used.
    - [X] The third paragraph of the second page: "They also leveraged
          WordNet ..." This is the first time "WordNet" is mentioned
          without having been introduced before.
          - reponse: we moved the refs around in previous work
    - [X] The parag

This paper makes the following contributions: 
\begin{itemize}
\item introduces the concept of labelled topic extraction, using a non-functional requirements (NFR) taxonomy for our labels; 
\item evaluates an unsupervised method of automated topic labelling (word-lists);
%\item Our unsupervised method can be applied to projects without training;
\item evaluates a supervised method of automatically labelling topics with a single NFR (machine learning);
\item evaluates a supervised method of labelling topics with multiple NFRs (multi-label machine learning);
\item provides a method of cross-project analysis via topic labelling; and
\item applies these techniques to visualize NFRs over time, and to analyze maintenance activities.
\end{itemize}

>>>>

This paper makes the following contributions: 
\begin{itemize}
\item introduces the concept of labelled topic extraction, using a non-functional requirements (NFR) taxonomy for our labels;

%\item evaluates an unsupervised method of automated topic labelling (word-lists);
%%\item Our unsupervised method can be applied to projects without training;
%%\item 
%evaluates a supervised method of automatically labelling topics with a single NFR (machine learning);
%%\item 
%evaluates a supervised method of labelling topics with multiple NFRs
%(multi-label machine learning);

\item evaluates three kinds of automatic topic labelling methods:
  semi-unsupervised labelling (word-lists) of topics, supervised labelling of
  topics with a single NFR (machine learning), 
  and supervised labelling of topics with multiple NFRs (multi-label
  machine learning)

%  of automated topic labelling (word-lists);
%\item Our unsupervised method can be applied to projects without training;
%\item 
%evaluates a supervised method of automatically labelling topics with a single NFR (machine learning);
%\item 
%evaluates a supervised method of labelling topics with multiple NFRs (multi-label machine learning);

\item provides a method of cross-project analysis via topic labelling; and
 applies these techniques to visualize NFRs over time, and to analyze maintenance activities.
\end{itemize}
